Equations & R Code

### 2016-12-29 manuscript/coexistence-stability_ms.Rmd
tiny edits to ms intro

\noindent \textbf{Number of Words}: 3,698

@@

Fluctuating environmental conditions are an important ingredient for stable species coexistence, both in theoretical models [@Chesson2000; @Chesson2004] and in natural communities [@Caceres1997; @Descamps-Julien2005; @Adler2006; @Angert2009].
Such "fluctuation-dependent" coexistence requires that species have unique environmental responses and that environmental conditions vary so that each species in a community experiences favorable and unfavorable conditions, which prevents competitive exclusion [@Chesson2000].
When coexistence is maintained by a fluctuation-dependent mechanism, an increase in environmental variability might lead to an increase in species richness and, consequently, a decrease in ecosystem variability.
However, increasing environmental variability may also increase ecosystem variability by increasing the fluctuations of individual species, regardless of species richness. These countervailing effects of environmental variability present an interesting paradox: while increasing variability should increase ecosystem variability, that decrease might be offset by an increase in richness. Such a paradox complicates predictions about how ecosystems will respond to predicted departures from historical ranges of environmental variability.

>>>>

\noindent \textbf{Number of Words}: 3,699

@@

Fluctuating environmental conditions are an important ingredient for stable species coexistence, both in theoretical models [@Chesson2000; @Chesson2004] and in natural communities [@Caceres1997; @Descamps-Julien2005; @Adler2006; @Angert2009].
Such "fluctuation-dependent" coexistence requires that species have unique environmental responses and that environmental conditions vary so that each species in a community experiences favorable and unfavorable conditions, which prevents competitive exclusion [@Chesson2000].
When coexistence is maintained by a fluctuation-dependent mechanism, an increase in environmental variability might lead to an increase in species richness and, consequently, a decrease in ecosystem variability.
However, increasing environmental variability may also increase ecosystem variability by increasing the fluctuations of individual species, regardless of species richness. These countervailing effects of environmental variability present an interesting paradox: while increasing environmental variability should increase ecosystem variability, that increase might be offset by an increase in richness. Such a paradox complicates predictions about how ecosystems will respond to predicted departures from historical ranges of environmental variability.

### 2016-12-29 manuscript/coexistence-stability_ms.tex
tiny edits to ms intro

Fluctuating environmental conditions are an important ingredient for
stable species coexistence, both in theoretical models (Chesson 2000a,
Chesson et al. 2004) and in natural communities (C{á}ceres 1997,
Descamps-Julien and Gonzalez 2005, Adler et al. 2006, Angert et al.
2009). Such ``fluctuation-dependent'' coexistence requires that species
have unique environmental responses and that environmental conditions
vary so that each species in a community experiences favorable and
unfavorable conditions, which prevents competitive exclusion (Chesson
2000a). When coexistence is maintained by a fluctuation-dependent
mechanism, an increase in environmental variability might lead to an
increase in species richness and, consequently, a decrease in ecosystem
variability. However, increasing environmental variability may also
increase ecosystem variability by increasing the fluctuations of
individual species, regardless of species richness. These countervailing
effects of environmental variability present an interesting paradox:
while increasing variability should increase ecosystem variability, that
decrease might be offset by an increase in richness. Such a paradox
complicates predictions about how ecosystems will respond to predicted
departures from historical ranges of environmental variability.

>>>>

Fluctuating environmental conditions are an important ingredient for
stable species coexistence, both in theoretical models (Chesson 2000a,
Chesson et al. 2004) and in natural communities (C{á}ceres 1997,
Descamps-Julien and Gonzalez 2005, Adler et al. 2006, Angert et al.
2009). Such ``fluctuation-dependent'' coexistence requires that species
have unique environmental responses and that environmental conditions
vary so that each species in a community experiences favorable and
unfavorable conditions, which prevents competitive exclusion (Chesson
2000a). When coexistence is maintained by a fluctuation-dependent
mechanism, an increase in environmental variability might lead to an
increase in species richness and, consequently, a decrease in ecosystem
variability. However, increasing environmental variability may also
increase ecosystem variability by increasing the fluctuations of
individual species, regardless of species richness. These countervailing
effects of environmental variability present an interesting paradox:
while increasing environmental variability should increase ecosystem
variability, that increase might be offset by an increase in richness.
Such a paradox complicates predictions about how ecosystems will respond
to predicted departures from historical ranges of environmental
variability.
